Scipion Tailored for TEM Facilities: Image Processing in Streaming

### 2018-02-20 6.acknowledgments.tex
Updates from ShareLaTeX
ROB: done with the editing prior to 28 Feb meeting

    AFTER THIS LINE I JUST SAVED SOME TEXT THAT MAY BE USEFUL IN THE FUTURE DISREGARD THIS MATERIAL
   --------------------

\section{Getting Started}

\section{Project stability and funding. getting started}

Scipion and ScipionBox development is been done in the context of the Instruct Image Processing Cen-
ter (I2PC, http://i2pc.cnb.csic.es). Instruct is the European initiative for Strategic
Scientific Infrastructures (ESFRI) for Structural Biology. The I2PC started with the objective 
to provide efficient support for research projects in Europe demanding expertise in 
electron microscopy image processing. In order to support a large collection
of projects, the first activities of the I2PC were oriented to design and implement the
necessary software tools.

>>>>

----------------

    AFTER THIS LINE I JUST SAVED SOME TEXT THAT MAY BE USEFUL IN THE FUTURE DISREGARD THIS MATERIAL

    --------------------

\section{Project stability and funding}

Scipion development is been done in the context of the Instruct Image Processing Cen-
ter (I2PC, http://i2pc.cnb.csic.es). Instruct is the European initiative for Strategic
Scientific Infrastructures (ESFRI) for Structural Biology. The I2PC started with the objective 
to provide efficient support for research projects in Europe demanding expertise in 
electron microscopy image processing. In order to support a large collection
of projects, the first activities of the I2PC were oriented to design and implement the
necessary software tools.
